{\it E}nKCF: Ensemble of Kernelized Correlation Filters for High-Speed Object Tracking

### 2017-11-28 wacv_for_review.tex
More typos fixed, and grammar mistakes corrected

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and then estimate correct scale. For
example, Zhang and his colleagues used the MOSSE tracker
\cite{bolme2010visual} to estimate the target's translation. And then
they attempted to update the scale of the target by further analyzing
image, sub-regions in high confidence. Their method is based on an
assumption that the scale of a target would not change much over two
consecutive frames. Similarly, Ma and his colleagues used two KCFs to
learn the translation and scale of a target separately
\cite{ma2015long}. In particular, a KCF is used to learn the
translation of the target and its background. Given this, another KCF
is used to learn the target area to estimate a new scale of the
target. However, because of running more than a KCF on each frame,
this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. To maximize run-time
performance and accuracy, instead of running them all together on
every frame, we deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, our method aims at addressing scale
change and estimate target's motion efficiently while maintaining or
increasing run-time performance. Figure \ref{Workflows} illustrates
the workflow of the {\it E}nKCF.

@@

\begin{algorithm*}[h]
\small
\DontPrintSemicolon
\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, complete cycle of scale filter $n = 5$,}
\KwOut{	\uIf{$fc\:\%\:n=0$ (\textbf{Condition 1})}
			{
				Estimated Target State $(x_{t},y_{t},s_{t})$,
				Scale filter (\textit{target-only}) model $R_{s}$
			}
			 \ElseIf{$fc\:\%\:n>0\:\:and\:\:fc\:\%\:n\leq n/2$ (\textbf{Condition 2})}
			 {
				Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
			  	Large Area Translation Filter model $R_{t}^{L}$
			}			 
			 \Else (\textit{\textbf{Condition 3}})
			{			 
				 Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
				Small Area Translation Filter model $R_{t}^{S}$			
			}	
		}
\SetKwBlock{Begin}{function}{end function}
\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
{
 	// \textit{Translation Estimation - Particle Filter} \\
	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $\mathbf{(x_{t},y_{t},s_{t-1})}$ \\
     // \textit{Translation Estimation - Correlation Filter} \\
	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
	// \textit{Scale Estimation - Correlation Filter}\\
	Scale pool for $R_{s}$ : $\mathbf{S} = \lbrace1.05,1.0,1/1.05\rbrace$,\\
	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\ 
	Skip it for $R_{t}^{L}$ (Condition 2) and $R_{t}^{S}$ (Condition 3), $\mathbf{s_{t}}$=$\mathbf{s_{t-1}}$\\
	// \textit{Update Translation - Particle Filter}\\
	Do Importance Re-sampling (if necessary) and compute the 
	mean of posterior pdf $\mathbf{(x_{t},y_{t})}$\\
	// \textit{Model Update}\\
	Update $R_{t}^{S}$ (Condition 3),\\
	Update $R_{t}^{L}$ (Condition 2),\\
	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
		Update $R_{s}$ (Condition 1)}
  \label{endfor}
  \Return{($x_{t},y_{t},s_{t}$)}
}
\caption{{\it E}nKCF Tracking Algorithm}\label{alg:MKCF}
\end{algorithm*}

@@

The algorithm \ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
The order of running these three KCFs is important because each of
these filters aims at addressing different challenges. A translation
filter, $R_{t}^{L}$, is applied to the $i$th and $i$+$1$th image
frames, another translation filter, $R_{t}^{S}$ is applied to the
$i$+$2$th and $i$+$3$th image frames, and then the scale filter,
$R_{s}$ is applied to the $i$+$4$the image. This order repeats until
the last image is presented. Note that the translation filter,
$R_{t}^{L}$, is intended to run right after the scale filter, $R_s$,
runs which is applied at every other $i$+$4$ frames. We run these
filters in this way because we want to minimize any drifts that are
likely to happen running only $R_{s}$. In addition, the filter,
$R_{t}^{S}$, is applied to every other two frames before $R_{s}$ and
right after two consecutive frames running $R_{t}^{L}$. By repeating
this order of learning three KCFs, we can integrate more
discriminative shape features that cannot be learned just by
$R_{t}^{L}$. The filter, $R_{t}^{L}$, uses shape and color information
together to recover from any potential drifts -- drifts could happen
only looking the target's scale by the filter, $R_{s}$.

@@

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E(h) = \frac{1}{2}||\mathbf{y}-\sum_{c=1}^{C}\mathbf{h_{c}}*\mathbf{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\mathbf{h_{c}}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where $\mathbf{y}$ represents the desired continuous response whereas $\mathbf{h}$ and
$\mathbf{x_{c}}$ represents the learned correlation filter and training
template for the given channel. The parameter $c$ enabled one to
integrate features in multiple channels, such as HoG and color, in
this setup \cite{henriques2015high,galoogahi2013multi}. A closed-form
solution for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
closed-form solution, an element-wise multiplication in
frequency domain was proposed for $\hat{w}$:
\begin{equation}
\mathbf{\hat{w}} = \mathbf{\hat{x}^{*}}*\mathbf{\hat{y}}(\mathbf{\hat{x}^{*}}*\mathbf{\hat{x}}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of this closed-form solution is proposed to increase robustness
to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized Fourier
domain dual form solution is expressed as
\begin{equation}
\mathbf{\hat{\alpha}} = \mathbf{\hat{y}}(\mathbf{\hat{k}^{xx}}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\lambda$ represents the regularization weight whereas $\mathbf{\hat{k}^{xx}}$ denotes
 the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and it is expressed as
\begin{equation}
\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'})))
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $\mathbf{w}$ and multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
Specifically, one can execute an object detection task using this kernelized correlation
filter with multi-channel features as
\begin{equation}
\mathbf{r(z)} = F^{-1}(\mathbf{\hat{k}^{xz}} \odot \mathbf{\hat{\alpha}})
\end{equation}
where $\mathbf{r}$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high and low
speed tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast} and ones in
relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, CCOT
\cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and
CCOT trackers originally uses deep convolutional features, however,
for the sake of fair comparison, we employ fHoG and color-naming
features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows
the results on the UAV123 dataset. The {\it E}nKCF outperformed other
high-speed trackers by $3\%$-$15\%$ at 20 pixels precision. Three
algorithms, SAMF, DSST, and Struck did about $5\%$ better than ours in
accuracy, but 10-20 times slower. The more recent trackers, ECO and
CCOT, on the other hand, outperforms {\it E}nKCF by $15\%$ while
running at 10-15 times slower speed.  For the scale adaptation, {\it
  E}nKCF did fourth best in terms of AUC for the success rate plot. It
outperformed other high-speed trackers by about $20\%$-$25\%$ in
AUC. In addition, it performed even better than some of the
lower-speed trackers.  For example, for AUC, {\it E}nKCF outperformed
Struck and DSST by $5\%$ and $10\%$ while running at more than $10$
and $30$ times faster.

@@

On the lower frame rate dataset ($10$ fps), the ECO and CCOT's
precision rates drop about $10\%$ worse than the original dataset. We
believe that this is an indicator of how good of a performance can be
expected from these trackers on a limited hardware. The projected
frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5
and $\simeq$0.3 by using our convention described in
section~\ref{introduction}. In this case, it would be reasonable to
expect these trackers to perform drastically worse on such hardware
whereas the {\it E}nKCF can still perform similarly due to its
real-time speed on a low-end hardware. Our observations are also
supported by \cite{mueller2017context} that evaluates the correlation
filter-driven trackers at variable frame rates matching their
operation rates.

>>>>

Another way of handling the scale change for the correlation filter
based approach is to estimate a correct scale at a location where a
target highly likely appears \cite{zhang2014fast} -- estimate a
target's translation first and then estimate correct scale. For
example, Zhang and his colleagues used the MOSSE tracker
\cite{bolme2010visual} to estimate the target's translation. And then
they attempted to update the scale of the target by further analyzing
image sub-regions in high confidence. Their method is based on an
assumption that the scale of a target would not change much over two
consecutive frames. Similarly, Ma and his colleagues used two KCFs to
learn the translation and scale of a target separately
\cite{ma2015long}. In particular, a KCF is used to learn the
translation of the target and its background. Given this, another KCF
is used to learn the target area to estimate a new scale of the
target. However, because of running more than a KCF on each frame,
this method degrades its run-time performance (i.e., $\leq 50
fps$). Our method is motivated by this idea -- the idea of deploying
multiple KCFs to address the issues of single target tracking: scale
and translation, but in a more efficient way. To maximize run-time
performance and accuracy, instead of running them all together on
every frame, we deploy three KCFs in turn:
\textit{target}+\textit{small background} translation filter
($R_{t}^{S}$), \textit{target-only} scale filter ($R_{s}$) and
\textit{target}+\textit{large background} translation filter
($R_{t}^{L}$). By doing so, our method aims at addressing scale
change and estimate target's motion efficiently while maintaining or
increasing run-time performance. Figure \ref{Workflows} illustrates
the workflow of the {\it E}nKCF.

@@

\begin{algorithm*}[h]
\small
\DontPrintSemicolon
\KwIn{ Initial bounding box $(x_{0},y_{0},s_{0})$, frame counter $fc$, complete cycle of scale filter $n = 5$,}
\KwOut{	\uIf{$fc\:\%\:n=0$ (\textbf{Condition 1})}
			{
				Estimated Target State $(x_{t},y_{t},s_{t})$,
				Scale filter (\textit{target-only}) model $R_{s}$
			}
			 \ElseIf{$fc\:\%\:n>0\:\:and\:\:fc\:\%\:n\leq n/2$ (\textbf{Condition 2})}
			 {
				Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
			  	Large Area Translation Filter model $R_{t}^{L}$
			}			 
			 \Else (\textit{\textbf{Condition 3}})
			{			 
				 Estimated Target State $(x_{t},y_{t},s_{t} = s_{t-1})$,
				Small Area Translation Filter model $R_{t}^{S}$			
			}	
		}
\SetKwBlock{Begin}{function}{end function}
\Begin($\text{track($x_{t-1},y_{t-1},s_{t-1}$) }$)
{
 	// \textit{Translation Estimation - Particle Filter} \\
	Transit Particle Filter to the frame $t$ and compute the mean of prior pdf $\mathbf{(x_{t},y_{t},s_{t-1})}$ \\
     // \textit{Translation Estimation - Correlation Filter} \\
	Crop the ROI for the $R_{t}^{L}$ (Condition 2), or $R_{t}^{S}$ (Condition 3) given $(x_{t},y_{t})$ and estimate new position as $\mathbf{(x_{t},y_{t})}$ = $\mathbf{\textit{max}(y_{R_{t}})}$\\
	// \textit{Scale Estimation - Correlation Filter}\\
	Scale pool for $R_{s}$ : $\mathbf{S} = \lbrace1.05,1.0,1/1.05\rbrace$,\\
	Crop the ROI for the $R_{s}^{i}$ (Condition 1) and estimate scale factor, $\mathbf{\alpha}$ = $\mathbf{\underset{i\in S}{\textit{argmax}}(PSR(y_{R_{s}^{i}}))}$, and new scale $\mathbf{s_{t} = \alpha * s_{t-1}}$,\\ 
	// \textit{Update Translation - Particle Filter}\\
	Do Importance Re-sampling (if necessary) and compute the 
	mean of posterior pdf $\mathbf{(x_{t},y_{t})}$\\
	// \textit{Model Update}\\
	Update $R_{t}^{S}$ (Condition 3),\\
	Update $R_{t}^{L}$ (Condition 2),\\
	\uIf{$PSR(y_{R_{s}}) \geq T_{R_{s}}$}{
		Update $R_{s}$ (Condition 1)}
  \label{endfor}
  \Return{($x_{t},y_{t},s_{t}$)}
}
\caption{{\it E}nKCF Tracking Algorithm}\label{alg:MKCF}
\end{algorithm*}

@@

The algorithm \ref{alg:MKCF} shows the pseudo-code of {\it E}nKCF.
The order of running these three KCFs is important because each of
these filters aims at addressing different challenges. A translation
filter, $R_{t}^{L}$, is applied to the $i$th and $i$+$1$th image
frames, another translation filter, $R_{t}^{S}$ is applied to the
$i$+$2$th and $i$+$3$th image frames, and then the scale filter,
$R_{s}$ is applied to the $i$+$4$th image. This order repeats until
the last image is presented. Note that the translation filter,
$R_{t}^{L}$, is intended to run right after the scale filter, $R_s$,
runs which is applied at every other $i$+$4$ frames. We run these
filters in this way because we want to minimize any drifts that are
likely to happen running only $R_{s}$. In addition, the filter,
$R_{t}^{S}$, is applied to every other two frames before $R_{s}$ and
right after two consecutive frames running $R_{t}^{L}$. By repeating
this order of learning three KCFs, we can integrate more
discriminative shape features that cannot be learned just by
$R_{t}^{L}$. The filter, $R_{t}^{L}$, uses shape and color information
together to recover from any potential drifts -- drifts could happen
only looking the target's scale by the filter, $R_{s}$.

@@

The KCF solves essentially the problem of a regression in the form of
the regularization (ridge regression):
\begin{equation}
E(h) = \frac{1}{2}||\mathbf{y}-\sum_{c=1}^{C}\mathbf{h_{c}}*\mathbf{x_{c}}||^{2} + \frac{\lambda}{2}\sum_{c=1}^{C}||\mathbf{h_{c}}||^{2}
\label{eq:Closedform_RidgeReg}
\end{equation}
where we seek for $\mathbf{h}$ that minimizes $E$ given the desired 
continuous response, $\mathbf{y}$, and the training template $\mathbf{x}$. 
The parameter $c$ enables one to integrate features in the form of 
multiple channels, such as HoG and color, in this setup \cite{henriques2015high,galoogahi2013multi}. 
A closed-form solution for Equation \ref{eq:Closedform_RidgeReg} exists. To simplify the
closed-form solution, an element-wise multiplication in
frequency domain was proposed to learn the frequency domain correspondence of $\mathbf{h}$, $\mathbf{\hat{w}}$:
\begin{equation}
\mathbf{\hat{w}} = \mathbf{\hat{x}^{*}}*\mathbf{\hat{y}}(\mathbf{\hat{x}^{*}}*\mathbf{\hat{x}}+\lambda)^{-1}.
\label{eq:DiagonalizedPrimalSolution}
\end{equation}
A non-linear version of $\mathbf{\hat{w}}$, $\mathbf{\hat{\alpha}}$ , is proposed to increase robustness
to any geometric and photometric variations
\cite{henriques2015high}. In particular, the diagonalized non-linear Fourier
domain dual form solution is expressed as
\begin{equation}
\mathbf{\hat{\alpha}} = \mathbf{\hat{y}}(\mathbf{\hat{k}^{xx}}+\lambda)^{-1}
\label{eq:FourierDualDomainSolution}
\end{equation}
where $\lambda$ represents the regularization weight whereas $\mathbf{\hat{k}^{xx}}$ denotes
 the first row of the kernel matrix $\mathbf{K}$ known as \textit{gram matrix} and is expressed as
\begin{equation}
\mathbf{k^{xx^{'}}} = exp(-\dfrac{1}{\alpha^{2}}(||\mathbf{x}||^{2}+||\mathbf{x}^{'}||^{2}-2F^{-1}(\sum^{C}_{c}\mathbf{\hat{x}_{c}}^{*}\odot \mathbf{\hat{x}_{c}}^{'}))).
\label{eq:GaussianCorrelationSingleChannel}
\end{equation}
An early version based on this formulation used grayscale feature
($C=1$) to learn the solution vector $\mathbf{w}$ and integrating multi-channel features
such as HoG and Color showed improved accuracy
\cite{henriques2015high,galoogahi2013multi,tang2015multi,ma2015long,bibi2015multi}. 
In the detection phase,  the learned correlation filter is correlated with the first row of the gram matrix,
$\mathbf{k^{xz^{'}}}$, which contains the similarity values between the learned feature template $\mathbf{x}$
and the new test template $\mathbf{z}$. This can be formulated as
\begin{equation}
\mathbf{r(z)} = F^{-1}(\mathbf{\hat{k}^{xz}} \odot \mathbf{\hat{\alpha}})
\end{equation}
where $\mathbf{r}$ denotes the correlation response at all cyclic shifts of the
first row of the kernel matrix.

In practice, the solution vector, $\mathbf{\hat{\alpha}}$, and 
the feature template matrix, $\mathbf{x}$, are accumulated over time
to integrate temporal information as
\begin{align}
 \mathbf{\hat{\alpha}_{t}} =  (1 - \beta)  \mathbf{\hat{\alpha}_{t-1}} +  \beta \mathbf{\hat{\alpha}_{t}} \\
  \mathbf{x_{t}} =  (1 - \beta)  \mathbf{x_{t-1}} + \beta  \mathbf{x_{t}}
\end{align}

where $\beta$ is the learning rate and mostly tuned to a small value.

@@

\textbf{Performance on UAV123 Dataset} We used the precision and
success rate to compare the performance of the proposed algorithm with
those of the state-of-the-art, online algorithms for high and low
speed tracking. For the precision, we rank the trackers based on the
precision numbers at 20 pixels whereas in the success rate plots,
trackers are ranked based on area under curve (AUC) scores. The
tracking algorithms under the comparison include ones in high-speed
($\geq$300 fps): KCF \cite{henriques2015high}, CSK
\cite{henriques2012exploiting}, DCF \cite{henriques2015high}, MOSSE
\cite{bolme2010visual}, and STC \cite{zhang2014fast} and ones in
relatively lower-speed ($\geq$50): ECO \cite{DanelljanCVPR2017}, CCOT
\cite{DanelljanECCV2016}, SCT \cite{Choi_2016_CVPR}, SAMF
\cite{li2014scale}, DSST \cite{danelljan2014accurate}, Struck
\cite{hare2012efficient}, MUSTER \cite{hong2015multi}, TLD
\cite{kalal2012tracking}, and OAB \cite{zhang2012robust}. The ECO and
CCOT trackers originally uses deep convolutional features, however,
for the sake of fair comparison, we employ fHoG and color-naming
features similar to our tracker. Figure \ref{fig:UAV123_DATASET} shows
the results on the UAV123 dataset. The {\it E}nKCF outperformed other
high-speed trackers by $3\%$-$15\%$ at 20 pixels precision. Three
algorithms, SAMF, DSST, and Struck did about $5\%$ better than ours in
accuracy, but 10-20 times slower. The more recent trackers, ECO and
CCOT, on the other hand, outperforms {\it E}nKCF by $15\%$ while
running at 10-15 times slower speed.  For the scale adaptation, {\it
  E}nKCF did fourth best in terms of AUC for the success rate plot. It
outperformed other high-speed trackers by about $20\%$-$25\%$ in
AUC. In addition, it performed even better than some of the
lower-speed trackers.  For example, for AUC, {\it E}nKCF outperformed
Struck and DSST by $5\%$ and $10\%$ while running at more than $10$
and $30$ times faster. We believe that there can be two reasons why {\it E}nKCF
outperforms the DSST that updates the scale every frame searching over
33 scale ratios. (1) The DSST uses a 1-D scale filter whereas ours applies a 2-D scale
filter. This might reduce the spatial information learned in the scale filter. (2) The
DSST scale filter originally employs only fHoG features whereas ours combines
both fHoG and color-naming features.

@@

On the lower frame rate dataset ($10$ fps), the ECO and CCOT's
precision rates drop about $10\%$ than the original dataset. We
believe that this is an indicator of how good of a performance can be
expected from these trackers on a limited hardware. The projected
frame rates of the ECO and CCOT on a low-end hardware are $\simeq$1.5
and $\simeq$0.3 by using our convention described in
section~\ref{introduction}. In this case, it would be reasonable to
expect these trackers to perform drastically worse on such hardware
whereas the {\it E}nKCF can still perform similarly due to its
real-time speed on a low-end hardware. Our observations are also
supported by \cite{mueller2017context} that evaluates the correlation
filter-driven trackers at variable frame rates matching their
operation rates.
